---
title: "Work Shop Preparation"
author: "Zachary M. Smith"
date: "February 19, 2019"
output:
  html_document: default
---

# Installation Links

Please install R and RStudio by following the links below.
```{r, echo=FALSE}
urls <- c("https://cran.r-project.org/bin/windows/base/",
          "https://www.rstudio.com/products/rstudio/download/#download")
link.df <- data.frame(
  Software = c("R", "RStudio"),
  Link = paste0("[", urls, "](", urls, ")")
)

knitr::kable(link.df)
```

## Updating Software and Packages

### R

For Windows Operating Systems, run the following code in the RGui, __NOT__ in RStudio. The RGui should be installed when you install R. On my Windows machine, I access RGui by clicking on the R program file-- my current file name is "R x64 3.6.2".

<center>
<video width="960" height="540" controls>
  <source src="images/2019-12-23_14-11-24.mp4" type="video/mp4">
</video>
</center>

Once you have the RGui open, copy and paste the R code below into the R Console window. Make sure R Studio is closed before running this code within the RGui. Hit enter once to install the __installr__ package. Hit enter a second time to run the __installer__ package function `updateR()` and follow the instructions.

This code was copied from: https://www.r-statistics.com/2013/03/updating-r-from-r-on-windows-using-the-installr-package/). 
```{r, eval=FALSE}
# installing/loading the package:
if(!require(installr)) {
install.packages("installr");
require(installr)
} #load / install+load installr

# using the package:
updateR()
```

### RStudio

1. Open RStudio
2. Click on "Help" on the toolbar
3. Click on "Check for Updates"
4. Follow instructions 

<center>
<video width="960" height="540" controls>
  <source src="images/rstudio_updates_final.mp4" type="video/mp4">
</video>
</center>

### R-Packages

1. Open RStudio
2. Click on "Tools" on the toolbar
3. Click on "Check for Package Updates…"
4. Follow instructions 

<center>
<video width="960" height="540" controls>
  <source src="images/update_packages.mp4" type="video/mp4">
</video>
</center>

#### Packages for Workshop

Please run the following code within RStudio to make sure you have all of necessary packages for this workshop installed.

1. Open RStudio
2. Copy the following code

```{r, eval=FALSE}
package.vec <- c("tidyverse", "lubridate",
                 "knitr", "rmarkdown", "markdown", "bookdown", "caTools", "bitops",
                 "DT", "leaflet", "shiny", "jsonlite", "plotly",
                 "data.table", "rprojroot", "viridis")

install.packages(package.vec)
```

3. Paste the code into the Console within RStudio
4. Hit Enter
    + If prompted with "Do you want to restart R prior to installing?", select "Yes"
    + If prompted again then select "No"
5. The packages should begin to install. This may take some time.


<center>
<video width="960" height="540" controls>
  <source src="images/install_workshop_packages.mp4" type="video/mp4">
</video>
</center>


