--- 
title: "R Markdown Crash Course"
author: "Zachary M. Smith"
date: "`r Sys.Date()`"
site: "bookdown::bookdown_site"
output:
  bookdown::gitbook: default
documentclass: book
biblio-style: apalike
link-citations: yes
---

# Preparation for Workshop

Please follow the instructions in this section prior to attending the 2020 NABs conference.

## Install R and R Studio

Please install R and R Studio by following the links below.
```{r, echo=FALSE}
urls <- c("https://cran.r-project.org/bin/windows/base/",
          "https://www.rstudio.com/products/rstudio/download/#download")
link.df <- data.frame(
  Software = c("R", "R Studio"),
  Link = paste0("[", urls, "](", urls, ")")
)

knitr::kable(link.df)
```

## Updating Software and Packages

### R

For Windows Operating Systems, run the following code in the RGui, __NOT__ in R Studio. The RGui should be installed when you install R. On my Windows machine, I access RGui by clicking on the R program file-- my current file name is "R x64 3.6.2".

<center>
<video width="960" height="540" controls>
  <source src="images/2019-12-23_14-11-24.mp4" type="video/mp4">
</video>
</center>

Once you have the RGui open, copy and paste the R code below into the R Console window. Make sure R Studio is closed before running this code within the RGui. Hit enter once to install the __installr__ package. Hit enter a second time to run the __installer__ package function `updateR()` and follow the instructions.

This code was copied from: https://www.r-statistics.com/2013/03/updating-r-from-r-on-windows-using-the-installr-package/). 
```{r, eval=FALSE}
# installing/loading the package:
if(!require(installr)) {
install.packages("installr");
require(installr)
} #load / install+load installr

# using the package:
updateR()
```

### R Studio

1. Open R Studio
2. Click on "Help" on the toolbar
3. Click on "Check for Updates"
4. Follow instructions 

<center>
<video width="960" height="540" controls>
  <source src="images/rstudio_updates_final.mp4" type="video/mp4">
</video>
</center>

### R-Packages

1. Open R Studio
2. Click on "Tools" on the toolbar
3. Click on "Check for Package Updates…"
4. Follow instructions 

<center>
<video width="960" height="540" controls>
  <source src="images/update_packages.mp4" type="video/mp4">
</video>
</center>

#### Packages for the Workshop

Please run the following code within R Studio to make sure you have all of necessary packages for this workshop installed.

1. Open R Studio
2. Copy the following code

```{r, eval=FALSE}
package.vec <- c("tidyverse", "lubridate",
                 "knitr", "rmarkdown", "markdown", "bookdown", "caTools", "bitops",
                 "DT", "leaflet", "shiny", "jsonlite", "plotly",
                 "data.table", "rprojroot", "viridis")

install.packages(package.vec)
```

3. Paste the code into the Console within R Studio
4. Hit Enter
    + If prompted with "Do you want to restart R prior to installing?", select "Yes"
    + If prompted again then select "No"
5. The packages should begin to install. This may take some time.


<center>
<video width="960" height="540" controls>
  <source src="images/install_workshop_packages.mp4" type="video/mp4">
</video>
</center>


