---
title: "Untitled"
author: "Zachary M. Smith"
date: "2/28/2020"
output: html_document
---

# Import Data

Import Zachary M. Smith's thesis data provided by Zachary M. Smith at the R Markdown Crash Course Workshop on March 3rd, 2020.

* `unique_id` (character) unique sample ID
* `lake` (character) lake code: caz = Cazenovia lake, onon = Onondaga, and ot = Otisco
* `lat` (numeric) latitude of sampling location
* `long` (numeric) longitude of sampling location
* `substrate_size_d50` (numeric) median partical size from pebble count
* `conductivity` (numeric) specific conductivity (µS/cm)
* `richness` (numeric) taxonomic richness
* `shannon` (numeric) Shannon-Wiener diversity index values
* `pct_ephemeroptera` (numeric) relative abundance of Ephemeroptera taxa
* `pct_amphipoda` (numeric) relative abundance of Amphipoda taxa
* `pct_diptera` (numeric) relative abundance of Diptera taxa
* `dom_1` (numeric) relative abundance of the most dominant taxon observed in each sample
```{r import-data}
thesis.df <- read.csv(file.path(here::here(),
                                "data",
                                "zms_thesis_metrics.csv"),
                      stringsAsFactors = FALSE)
```


# Preprocessing

Load the __tidyverse__ packages into the global environment.
```{r load-packages, message=FALSE}
library(tidyverse)
```

```{r prep-lake}
thesis.df <- thesis.df %>% 
  mutate(lake = case_when(
    lake %in% "caz" ~ "Cazenovia",
    lake %in% "onon" ~ "Onondaga",
    lake %in% "ot" ~ "Otisco",
    TRUE ~ "ERROR"
  ),
  lake = factor(lake, levels = c("Onondaga",
                                 "Otisco",
                                 "Cazenovia")))
```

For more details about the __DT__ package visit https://rstudio.github.io/DT/.
```{r dt}
library(DT)

datatable(thesis.df, options = list(scrollX = TRUE))
```
