---
title: "R Markdown Crash Course Example"
author: "Zachary M. Smith"
date: "2/26/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: journal
---
# lakedata
* unique_id (character) unique sample ID
```{r import, message=FALSE}
thesis.df <- read.csv(file = file.path("data", "zms_thesis_metrics.csv"), stringsAsFactors = FALSE)
```

```{r}
library(tidyverse)
```
```{r}
thesis.df <- thesis.df %>% 
  mutate(lake = case_when(
    lake %in% "caz" ~ "Cazenovia",
    lake %in% "onon" ~ "Onondaga",
    lake %in% "ot" ~ "Otisco",
    TRUE ~ "ERROR"
  ),
  lake = factor(lake, levels = c("Onondaga",
                                 "Otisco",
                                 "Cazenovia")))
```
```{r}
knitr::opts_chunk$set(fig.width = 8, fig.height = 4)
```
```{r}
ggplot(thesis.df, aes(substrate_size_d50, pct_diptera, color = lake)) +
  geom_point()
```
```{r}
ggplot(thesis.df, aes(lake, richness, fill = lake)) +
  geom_boxplot()
```




thesis.df <- thesis.df %>% 
  mutate(lake = case_when(
    lake %in% "caz" ~ "Cazenovia",
    lake %in% "onon" ~ "Onondaga",
    lake %in% "ot" ~ "Otisco",
    TRUE ~ "ERROR"
  ),
  lake = factor(lake, levels = c("Onondaga",
                                 "Otisco",
                                 "Cazenovia")))

# Introduction

This document was created during the _2020 NABs R Markdown workshop_ and will serve as an example workflow for my future use of __R Markdown__.

# Workflow

1. Open R Studio
2. Create an R Project
3. Add a data folder to the R project directory
4. Create an R Markdown document
5. Use Knit to compile the document.

# Import Data

# Preprocessing

[github link](https://rstudio.github.io/DT/)

```{r}
library(DT)
```

```{r}
datatable(thesis.df, options = list(scrollX = TRUE))
```


# Study Area

[maps](https://plot.ly/ggplot2/)



```{r}
library(leaflet)
```
```{r}
pal <- colorFactor(c("#619Cff", "#F8766D", "#00BA38"),
                   domain = c("Cazenovia", "Onondaga", "Otisco"))

leaflet(data = thesis.df,
        options = leafletOptions(minZoom = 7,
                                 maxZoom = 13)) %>% 
  addTiles() %>% 
  addCircleMarkers(~long, ~lat,
                   fillOpacity = 0.75,
                   fillColor = ~pal(lake),
                   stroke = FALSE,
             popup = paste("Sample ID:", thesis.df$unique_id, "<br/>",
                           "Lake:", thesis.df$lake, "<br/>",
                           "Latitude:", thesis.df$lat, "<br/>",
                           "Longitude:", thesis.df$long)
             )
```
```{r}
library(plotly)

scatter.plot <- ggplot(thesis.df, aes(substrate_size_d50, pct_diptera)) +
  geom_point(aes(color = lake)) +
  geom_smooth(method = "lm")

ggplotly(scatter.plot)
```


# Plot  {.tabset}

## Scatter Plot

## LOESS Plot

# Conclusions
